### 2020-05-17 README.Rmd
README

*  The regional boundaries are consistently used, coded and named - this will be harmonized with the package `regions` , currently under review in CRAN, which will help resolving common issues, and to properly join various Eurobarometer files with Eurostat data tables and Google data tables.

>>>>

*  The regional boundaries are consistently used, coded and named - this will be harmonized with the package [regions](http://regions.danielantal.eu/), currently under review in CRAN, which will help resolving common issues, and to properly join various Eurobarometer files with Eurostat data tables and Google data tables.
